---
title: "Uniform inference for multiple causal effects with invalid instruments"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to mvRobustIV}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 5, fig.height = 4)
```

```{r setup}
library(mvRobustIV)
```

## The problem

In multivariable instrumental-variable and Mendelian randomization analyses we
want a confidence region for a vector of causal effects `beta`, but some
instruments may violate the exclusion restriction and we do not know which.
Methods that first select a valid set and then condition on that choice can
undercover. `mvRobustIV` instead inverts validity tests on scalar residual
contrasts under a majority rule, giving a region with coverage at least
`1 - alpha` uniformly over a class that includes locally invalid instruments.

## A worked example

```{r}
sim <- simulate_mvmr(q = 2, p = 30, n_valid = 21, seed = 1)
attr(sim, "true_beta")
```

First-stage diagnostics tell us whether the region can be bounded:

```{r}
iv_diagnostics(sim)
```

The searching region and its coordinate sections:

```{r}
reg <- searching_region(sim)
reg
plot(reg)
```

Membership testing for any candidate vector:

```{r}
searching_membership(sim, attr(sim, "true_beta"))$in_region
searching_membership(sim, c(5, 5))$in_region
```

## When a coordinate is not identified

If fewer than a majority of instruments are individually strong for an
exposure, that coordinate is unbounded: the data do not identify it under
unknown invalidity. The conventional estimate may still look precise, but that
precision rests on assuming the selected instruments are valid.

```{r}
sim2 <- sim
sim2$se_X[6:30, 2] <- sim2$se_X[6:30, 2] * 20   # weaken exposure 2 for most SNPs
boundedness_rule(sim2)
suppressWarnings(searching_region(sim2))
```

## Comparators and refinement

```{r}
mv_ivw(sim)              # conventional inverse-variance-weighted estimate
tsht_valid_set(sim)$surplus
```

`sampling_region()` provides a resampling sensitivity check; the searching
region remains the default, since it carries the uniform guarantee.
